Embedding Dimension of Polyhedral Losses

### 2020-01-31 colt-20/embed-dim.tex
No idea

Note that a calibrated surrogate should also specify a link function $\psi: \reals^d \to \R$.
As our surrogate is an embedding, Theorem \ref{thm:embed-iff-poly} guarantees the existence of a link achieving calibration.
We can also easily construct one in the case of $d=1$, by taking the midpoints between the embedding points as cutoffs: $\psi(u) = \argmin_{r \in \R} |u - \varphi(r)|$, breaking ties arbitrarily.

>>>>

\jessiet{Cut next two lines for space}
%Note that a calibrated surrogate should also specify a link function $\psi: \reals^d \to \R$.
%As our surrogate is an embedding, Theorem \ref{thm:embed-iff-poly} guarantees the existence of a link achieving calibration.
We can easily construct a link function in the case of $d=1$, by taking the midpoints between the embedding points as cutoffs: $\psi(u) = \argmin_{r \in \R} |u - \varphi(r)|$, breaking ties arbitrarily.
